---
title: "Aaron Project 2"
author: "Aaron Rock"
date: "2022-10-19"
output: html_document
---
```{r init, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
library(gmodels)
library(ggplot2)
library(dplyr)
install.packages("matrixStats")
library(matrixStats)
library(corrplot)
library(FNN)
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```


```{r}
#First, load the file
online = data.frame(read.csv("online_shoppers_intention.csv"))
# We will use this dataframe later for model manipulation
original_online = data.frame(read.csv("online_shoppers_intention.csv"))
total_observations = nrow(online)
total_observations
head(online)
```
```{r, results='hide'}
# Handling categorical variables prior to plotting
online$Month = as.factor(online$Month)
online$Revenue = as.factor(online$Revenue)
online$Weekend = as.factor(online$Weekend)
online$VisitorType = as.factor(online$VisitorType)
```

``` {r}
monthFrequency = ggplot(online, aes(x=Month, color=Month, fill=Month)) + geom_bar() + labs(title="Count of Months",
        x ="Month", y = "Count")
monthFrequency
userCount = ggplot(online, aes(x=VisitorType, color=VisitorType, fill=VisitorType)) + geom_bar() + labs(title="Visitor Type Count",
        x ="Visitor Types", y = "Count")
userCount
revCount = ggplot(online, aes(x=Revenue, color=Revenue, fill=Revenue)) + geom_bar() + labs(title="Revenue Count",
        x ="Revenue", y = "Count")
revCount
revTrue = subset(online, online$Revenue == TRUE)
revFalse = subset(online, online$Revenue == FALSE)
pieNum <- c(nrow(revTrue), nrow(revFalse))
piepercent<- round(100*pieNum/sum(pieNum), 1)
pie(pieNum, labels = piepercent, main = "Revenue Percentages",col = rainbow(length(pieNum)))
legend("topright", c("True","False"), cex = 0.8, fill = rainbow(length(pieNum)))
```
```{r}
# Special Day data
specialDay = ggplot(online, aes(SpecialDay)) + geom_density(color="darkblue", fill="lightblue") + labs(title="Density Chart of Special Day",x ="Special Day", y = "Density")
specialDay
# scatterSpecialDay = ggplot(online, aes(Revenue, SpecialDay)) + geom_violin(), this plot had no significance
```

```{r}
admin = ggplot(online, aes(Administrative, color=Revenue, fill=Revenue)) + geom_histogram(bins=30) + labs(title="Count of Administrative", x ="Administrative", y = "Count")
admin
info = ggplot(online, aes(Informational, color=Revenue, fill=Revenue)) + geom_histogram(bins=30) + labs(title="Count of Informational", x ="Informational", y = "Count")
info
prod = ggplot(online, aes(ProductRelated, color=Revenue, fill=Revenue)) + geom_histogram(bins=30) + labs(title="Count of Product Related", x ="Product Related", y = "Count")
prod

#
# Duration of the above Pages
#

adminDur = ggplot(online, aes(Administrative_Duration, color=Revenue, fill=Revenue)) + geom_histogram(bins=30) + labs(title="Count of Administrative Duration", x ="Administrative Duration", y = "Count")
adminDur
infoDur = ggplot(online, aes(Informational_Duration, color=Revenue, fill=Revenue)) + geom_histogram(bins=30) + labs(title="Count of Informational Duration", x ="Informational Duration", y = "Count")
infoDur
prodDur = ggplot(online, aes(ProductRelated_Duration, color=Revenue, fill=Revenue)) + geom_histogram(bins=30) + labs(title="Count of Product Related Duration", x ="Product Related Duration", y = "Count")
prodDur
```

```{r}
# Bounce Rate is measured by total one page visits divided by total visits 
bounceBox = ggplot(online, aes(BounceRates)) + geom_boxplot(color='blue') + labs(title="Boxplot of Bounce Rate", x ="Bounce Rate")
bounceBox
# Exit Rate is measured by total exits from page divided by total visits to page
exitBox = ggplot(online, aes(ExitRates)) + geom_boxplot(color='orange') + labs(title="Boxplot of Exit Rate", x ="Exit Rate")
exitBox
# Page Value is the average value for a page that a user visited before landing on the goal page or completing an Ecommerce transaction
pageBox_rev = ggplot(revTrue, aes(PageValues)) + geom_boxplot(color='green') + labs(title="Boxplot of Page Values with Revenue", x ="Page Values")
pageBox_rev
pageBox_no_rev = ggplot(revFalse, aes(PageValues)) + geom_boxplot(color='red') + labs(title="Boxplot of Page Values of No Revenue Rows", x ="Page Values")
pageBox_no_rev
```
The average Bounce Rate for this site is `r mean(online$BounceRates)*100`%.
The average Exit Rate for this site is `r mean(online$ExitRates)*100`%.
Page Values that had revenue had an average of `r mean(revTrue$PageValues)`.
Page Values that had did not have revenue had an average of `r mean(revFalse$PageValues)`.
For our dataset it would be better to see individual page exit and bounce rates. The column variables Exit and Bounce Rates are the average of these metrics over each page on this site.


```{r}
# Corrplot after changing categorical to numerical
online_new = subset(online, select = -c(VisitorType, Month))
online_new$Weekend = as.numeric(online_new$Weekend)
online_new$Revenue = as.numeric(online_new$Revenue)
corrOnline <- cor(online_new)
corrplot(corrOnline, method="number",number.cex=0.5,tl.cex=.6)
```


```{r}
# Table for Month and Revenue of that Month
monthTable = xtabs( ~ Revenue + Month, data = online)
monthTable
chisqMonth = chisq.test(monthTable)
chisqMonth
```

```{r}
# Table for Special Day and Revenue as we get closer to that Day
# This value represents the closeness of the browsing date to special days or holidays
specialDayTable = xtabs( ~ Revenue + SpecialDay, data = online)
specialDayTable
chisqSD = chisq.test(specialDayTable)
chisqSD
```

```{r, results='hide'}
library(tidyr)
# Rehandle
online$VisitorType = as.factor(online$VisitorType)
online$Weekend = as.integer(online$Weekend)
online$OperatingSystems = as.integer(online$OperatingSystems)
online$Browser = as.integer(online$Browser)
online$TrafficType = as.integer(online$TrafficType)
online$Region = as.integer(online$Region)
online$Month = as.integer(factor(online$Month, levels = month.abb))
online = drop_na(online)
# Making Visitor Type into numerical variable
library(tidyverse)
online$VisitorType <- str_replace(online$VisitorType,'New_Visitor','1')
online$VisitorType <- str_replace(online$VisitorType,'Other','2')
online$VisitorType <- str_replace(online$VisitorType,'Returning_Visitor','3')
online$VisitorType = as.numeric(online$VisitorType)
```


```{r, results='hide'}
# PageValues + Month + ExitRates + ProductRelated_Duration + TrafficType + VisitorType + ProductRelated
original_online$VisitorType = as.factor(original_online$VisitorType)
original_online$Weekend = as.integer(original_online$Weekend)
original_online$OperatingSystems = as.integer(original_online$OperatingSystems)
original_online$Browser = as.integer(original_online$Browser)
original_online$TrafficType = as.integer(original_online$TrafficType)
original_online$Region = as.integer(original_online$Region)
original_online$Month = as.integer(factor(original_online$Month, levels = month.abb))
original_online = drop_na(online)
# Making Visitor Type into numerical variable

original_online$VisitorType <- str_replace(original_online$VisitorType,'New_Visitor','1')
original_online$VisitorType <- str_replace(original_online$VisitorType,'Other','2')
original_online$VisitorType <- str_replace(original_online$VisitorType,'Returning_Visitor','3')
original_online$VisitorType = as.numeric(original_online$VisitorType)

original_online = subset(original_online, select = -c(1,2,3,4,7,10,12,13,14,17))
```

```{r}
scaledOnline <- as.data.frame(scale(online[1:17], center = TRUE, scale = TRUE))
```

```{r}
# Selected Variables based off EDA
scaled_Online_select <- as.data.frame(scale(original_online[1:7], center = TRUE, scale = TRUE))
```

```{r}
set.seed(123)
online_sample <- sample(2, nrow(scaledOnline), replace=TRUE, prob=c(0.80, 0.20))
```

```{r}
# Selected Variables Model based off EDA
set.seed(123)
online_sample_selected <- sample(2, nrow(scaled_Online_select), replace=TRUE, prob=c(0.8, 0.2))
```


```{r}
online_training <- scaledOnline[online_sample==1, 1:17]
online_test <- scaledOnline[online_sample==2, 1:17]
```

```{r}
# Selected Variables Model based off EDA
online_training_selected <- scaled_Online_select[online_sample_selected==1, 1:7]
online_test_selected <- scaled_Online_select[online_sample_selected==2, 1:7]
```


```{r}
online_trainLabels <- online[online_sample==1, 18]
online_testLabels <- online[online_sample==2, 18]
```

```{r}
# Selected Variables Model based off EDA
online_trainLabels_selected <- original_online[online_sample_selected==1, 8]
online_testLabels_selected <- original_online[online_sample_selected==2, 8]
```

```{r, results='hide'}
ResultDf = data.frame( k=numeric(0), Total.Accuracy= numeric(0), row.names = NULL )

ResultDf_selected = data.frame( k=numeric(0), Total.Accuracy= numeric(0), row.names = NULL )
```

```{r}
for (kval in 5:25) {
  online_pred <- knn(train = online_training, test = online_test, cl=online_trainLabels, k=kval)
  onlinePREDCross <- CrossTable(online_testLabels, online_pred, prop.chisq = FALSE)
  print( paste("k = ", kval) )
  onlinePREDCross
  
  cm = confusionMatrix(online_pred, reference = online_testLabels ) 
  cmaccu = cm$overall['Accuracy']
  print( paste("Total Accuracy = ", cmaccu ) )
   
  cmt = data.frame(k=kval, Total.Accuracy = cmaccu, row.names = NULL )  
  ResultDf = rbind(ResultDf, cmt)
  print( xkabledply(   as.matrix(cm), title = paste("ConfusionMatrix for k = ",kval ) ) )
  print( xkabledply(data.frame(cm$byClass), title=paste("k = ",kval)) )
}
``` 

```{r}
# Selected Variable Model
for (kval in 10:30) {
  online_pred_selected <- knn(train = online_training_selected, test = online_test_selected, cl=online_trainLabels_selected, k=kval)
  onlinePREDCross_selected <- CrossTable(online_testLabels_selected, online_pred_selected, prop.chisq = FALSE)
  print( paste("k = ", kval) )
  onlinePREDCross_selected
  
  cm_selected = confusionMatrix(online_pred_selected, reference = online_testLabels_selected ) 
  cmaccu_selected = cm_selected$overall['Accuracy']
  print( paste("Total Accuracy = ", cmaccu_selected ) )
   
  cmt_selected = data.frame(k=kval, Total.Accuracy = cmaccu_selected, row.names = NULL )  
  ResultDf_selected = rbind(ResultDf_selected, cmt_selected)
  print( xkabledply(   as.matrix(cm_selected), title = paste("ConfusionMatrix for k = ",kval ) ) )
  print( xkabledply(data.frame(cm_selected$byClass), title=paste("k = ",kval)) )
}
``` 

```{r, results='markup'}
xkabledply(ResultDf, "Total Accuracy Summary")
# Selected Variable Model
xkabledply(ResultDf_selected, "Total Accuracy Summary")
```


```{r}
kPlot = ggplot(ResultDf, aes(k, Total.Accuracy)) + geom_point(colour = "blue", size = 3) + geom_line(color='orange')
kPlot

kPlot_selected = ggplot(ResultDf_selected, aes(k, Total.Accuracy)) + geom_point(colour = "blue", size = 3) + geom_line(color='orange')
kPlot_selected
```

```{r}
# Max Accuracy
online_pred_max <- knn(train = online_training, test = online_test, cl=online_trainLabels, k=15)
onlinePREDCross_max <- CrossTable(online_testLabels, online_pred, prop.chisq = FALSE)

# Selected Variable Model
online_pred_max_selected <- knn(train = online_training_selected, test = online_test_selected, cl=online_trainLabels_selected, k=25)
onlinePREDCross_max_selected <- CrossTable(online_testLabels_selected, online_pred_selected, prop.chisq = FALSE)
```


```{r}
loadPkg("pROC")
h <- roc(online_testLabels , as.integer(online_pred_max))
auc(h)
plot(h)

h_selected <- roc(online_testLabels_selected , as.integer(online_pred_max_selected))
auc(h_selected)
plot(h_selected)
```

Sadly, both models do not meet the cut off AUC metric of 0.8. We can see from the Confusion Matrix that when the models are at the optimal k value the total accuracy are in the high 80 percent levels. However, the issue we need to address is the 



